Replicator-mutator and noise-perturbed replicator dynamics

### 2014-09-18 snippets/data_exploration/data_exploration_tmp.Rmd
data exploration

data = read.csv('~/Desktop/data/svn/vagueness-games/results/20140916-133324.csv', 
                colClasses=c('numeric','factor','numeric','numeric','numeric',
                             'factor','numeric','numeric','numeric','numeric',
                             'numeric','numeric','numeric','numeric','numeric',
                             'numeric','factor','factor','character','character'))

ds = data[,c(1,4,7,8,9,10,11:16)] # only relevant data
dm = melt(ds,id.vars = c("Number.of.states", "Impairment")) # melted data

@@

pairs(~ Number.of.states + Impairment + Speaker.entropy + Hearer.entropy + Speaker.convexity +
        Speaker.Voronoiness + Hearer.Voronoiness +
        Speaker.informativity + Hearer.informativity + Expected.utility + Iterations, data=ds)
```

@@

dms = summarySE(dm, groupvars = c("Number.of.states", "Impairment", "variable"), measurevar="value")
dsub = subset(dms, !grepl("informativity",dms$variable) )

@@

sp + facet_wrap(~ variable, ncol=2, scales="free")

>>>>

data = read.csv('~/Desktop/data/svn/vagueness-games/results/20140918-142408.csv', 
                colClasses=c('numeric','factor','numeric','numeric','numeric',
                             'factor','numeric','numeric','numeric','numeric',
                             'numeric','numeric','numeric','numeric','numeric',
                             'numeric','numeric','numeric','character','character'))

ds = data[,c(1,4,5,7,8,11:17)] # only relevant data
dm = melt(ds,id.vars = c("Number.of.states", "Impairment", "Tolerance")) # melted data

@@

pairs(~ Number.of.states + Impairment + Tolerance + Speaker.entropy + Hearer.entropy + Speaker.convexity +
        Speaker.Voronoiness + Hearer.Voronoiness +
        Speaker.informativity + Hearer.informativity + Expected.utility + Iterations +
        Speaker.Convex.Cat, data=ds)
```

@@

dms = summarySE(dm, groupvars = c("Number.of.states", "Impairment", "Tolerance", "variable"), measurevar="value")
dsub = subset(dms, !grepl("informativity",dms$variable) )

@@

sp + facet_grid(variable ~ Tolerance, scales="free")
